An asymptotically normal out-of-sample test based on mixed estimation windows

### 2016-10-17 mixedwindow.tex
Make small change in proof of Theorem 1
[#18, #21] Add stubs for second and third part of Lemma A3's proof

\subsection{Proof of Theorem \ref{res:1}}
  Let $R'$ be a new sequence such that $R' \to \infty$ as $T \to \infty$
  and $R' = o(\sqrt{P})$, and then rewrite the centered \oos\ average as
  \begin{equation}\label{eq:6}
    \sqrt{P} (\fb - \E \fb^*)
    = \ocltb{t} ((f_t - \E f_t) + (\fh_t - f_t))
      + \tfrac{1}{\sqrt{P}} \osumc{t} (\fh_t - \E f_t).
  \end{equation}
  Lemma~\ref{res:a1} ensures that the second summation is $o_p(1)$, so
  we can use a Taylor expansion to rewrite~\eqref{eq:6} as
  \begin{align*}
    \sqrt{P} (\fb - \E \fb^*)
    &= \ocltb{t} (f_t - \E f_t) + F B \ocltb{t} H_t \\
    & \quad + \WesA + \WesB \\ & \quad + \WesC + \oclt{t} w_t + o_p(1)
  \end{align*}
  where $w_t$ equals $2 (\bh_t - \btrue)' x_t x_t' (\bh_t - \btrue)$.
  Lemma~\ref{res:a4} shows that
  \begin{gather}
    \WesA \to^{p} 0 \label{eq:11} \\
    \WesB \to^{p} 0 \label{eq:12} \\
    \intertext{and}
    \WesC \to^{p} 0 \label{eq:13}
  \end{gather}
  and Lemma~\ref{res:a2} along with the \clt\ ensures that $\oclt{t}
  w_t = o_{p}(1)$. The proof that
  \begin{equation*}
    \ocltb{t} (f_t - \E f_t) + F B \ocltb{t} H_t \to N(0, \sigma^2).
  \end{equation*}
  follows the same argument as in \citet{Wes:96} and \citet{Mcc:00}.

@@

\begin{proof}
We can write
\begin{equation*}
  \Big\lvert \WesA \Big\rvert \leq
  \Big\lVert \ocltb{t} (F_t - F) B \Big\rVert \;
  \omaxb{t} \lVert H_t \rVert.
\end{equation*}
From Lemma~\ref{res:a2}, $\omaxb{t} \lVert H_t \rVert \to^p
0$. \citepos{Jon:97} \clt\ implies that $\ocltb{t} (F_t - F) =
O_p(1)$, establishing~\eqref{eq:11}. The proofs of \eqref{eq:12}
and~\eqref{eq:13} are similar.
\end{proof}

>>>>

\subsection{Proof of Theorem \ref{res:1}}
  Let $R'$ be a new sequence such that $R' \to \infty$ as $T \to \infty$
  and $R' = o(\sqrt{P})$, and then rewrite the centered \oos\ average as
  \begin{equation}\label{eq:6}
    \sqrt{P} (\fb - \E \fb^*)
    = \ocltb{t} (\fh_t - \E f_t)
      + \tfrac{1}{\sqrt{P}} \osumc{t} (\fh_t - \E f_t).
  \end{equation}
  Lemma~\ref{res:a1} ensures that the second summation is $o_p(1)$, so
  we can rewrite~\eqref{eq:6} as
  \begin{align*}
    \sqrt{P} (\fb - \E \fb^*)
    &= \ocltb{t} (f_t - \E f_t) + F B \ocltb{t} H_t \\
    & \quad + \WesA + \WesB \\ & \quad + \WesC + \oclt{t} w_t + o_p(1)
  \end{align*}
  where $w_t$ equals $2 (\bh_t - \btrue)' x_t x_t' (\bh_t - \btrue)$.
  Lemma~\ref{res:a4} shows that
  \begin{gather}
    \WesA \to^{p} 0 \label{eq:11} \\
    \WesB \to^{p} 0 \label{eq:12} \\
    \intertext{and}
    \WesC \to^{p} 0 \label{eq:13}
  \end{gather}
  and Lemma~\ref{res:a2} along with the \clt\ ensures that $\oclt{t}
  w_t = o_{p}(1)$. The proof that
  \begin{equation*}
    \ocltb{t} (f_t - \E f_t) + F B \ocltb{t} H_t \to N(0, \sigma^2).
  \end{equation*}
  follows the same argument as in \citet{Wes:96} and \citet{Mcc:00}.

@@

\begin{proof}[Proof of~\eqref{eq:11}]
We can write
\begin{equation*}
  \Big\lvert \WesA \Big\rvert \leq
  \Big\lVert \ocltb{t} (F_t - F) B \Big\rVert \;
  \omaxb{t} \lVert H_t \rVert.
\end{equation*}
From Lemma~\ref{res:a2}, $\omaxb{t} \lVert H_t \rVert \to^p
0$. \citepos{Jon:97} \clt\ implies that $\ocltb{t} (F_t - F) =
O_p(1)$, establishing~\eqref{eq:11}.
\end{proof}

\begin{proof}[Proof of~\eqref{eq:12}]
TBD
\end{proof}

\begin{proof}[Proof of~\eqref{eq:13}]
TBD
\end{proof}
